---
output:
  pdf_document: default
  html_document: default
---
Research 2

Yun Seong Ji

```{r}
library(readxl)
```
```{r}
receipts <-read_excel("C:/Users/YunSeong/Downloads/2017-12-eeoc-harassment-charges-master/2017-12-eeoc-harassment-charges-master/data/SH_Charge_Receipts.xlsx")
```
```{r}
claim_industry <- read.csv("C:/Users/YunSeong/Downloads/2017-12-eeoc-harassment-charges-master/2017-12-eeoc-harassment-charges-master/output/d3_claims_by_industry.csv")
claim_sector<-read.csv("C:/Users/YunSeong/Downloads/2017-12-eeoc-harassment-charges-master/2017-12-eeoc-harassment-charges-master/output/d3_claims_by_sector.csv")
```
```{r}
information<-read.csv("C:/Users/YunSeong/Downloads/2017-12-eeoc-harassment-charges-master/2017-12-eeoc-harassment-charges-master/output/d3_information_naics_bls_info.csv")
```
```{r}
te<-information$total_employment
wp<-information$women_percentage
```
te: total employment 
wp: women percentage

```{r}
View(information)
```

```{r}
nw<-te*wp[2]
```
number of women
```{r}
nw
```
```{r}
normal<-te/100000
```
normal: total employment/1000000 --> normalize the number 
```{r}
industry<-information$industry
industry
```

```{r}
normal
```
```{r}
hours<-information$avg_hrly_earnings
```

```{r}
category<-claim_sector$naics_code
claim16<-claim_sector$claims_2016
totalclaim<-claim_sector$claims_total
```
```{r}
sum(totalclaim)
```

```{r}
sum<-sum(totalclaim)
```
```{r}
64443/sum
```
Approximately 38% of them did not specify an industry 
###ggplot 

```{r}
library(ggplot2)
```
```{r}
output1<-ggplot(claim_sector, aes(claim_sector$naics_code, claim_sector$claims_2016))+geom_bar(stat="identity", fill="darkblue")+scale_x_discrete("Industry")+scale_y_continuous("2016 claim")+theme_bw()+labs(title="Barchart")
```
```{r}
output1
```

The highest point is the unspecified one --> people still do not want to inform their workplaces in this situation. 


```{r}
output3<-ggplot(claim_sector, aes(claim_sector$naics_code, (claim_sector$claims_2016)/100000))+geom_bar(stat="identity", fill="darkblue")+scale_x_discrete("Industry")+scale_y_continuous("2016 claim")+theme_bw()+labs(title="Barchart")
```
```{r}
output3
```

```{r}
output2<-ggplot(claim_sector, aes(claim_sector$naics_code, claim_sector$claims_total))+geom_bar(stat="identity", fill="red")+scale_x_discrete("Industry")+scale_y_continuous("total claim")+theme_bw()+labs(title="Barchart")
```
```{r}
output2
```
```{r}
output4<-ggplot(claim_sector, aes(claim_sector$naics_code, (claim_sector$claims_total)/100000))+geom_bar(stat="identity", fill="red")+scale_x_discrete("Industry")+scale_y_continuous("total claim")+theme_bw()+labs(title="Barchart")
output4
```

```{r}
histogram1<-ggplot(data=claim_sector, aes(x=(totalclaim/100000), color=category))+geom_histogram(fill="white", bins=30)
```
```{r}
histogram1
```
```{r}
library("readxl")
```

```{r}
data3<-read_excel("C:/Users/YunSeong/Desktop/reaading and research/data3.xlsx")
```
```{r}
a<-data3$industry
b<-data3$claims_2016
c<-data3$claims_total
d<-data3$avg_hrly_earnings
e<-data3$total_employment
f<-data3$women_percentage
```
```{r}
h<-e/100000
```
```{r}
h
```

```{r}
d
```
```{r}
c/100000
```

```{r}
p<-ggplot(data3, aes(x=d, y=f, fill=a))+geom_bar(stat="identity")
```
```{r}
p
```
x-axis: average hourly earning, y-axis: women percentage per industry

```{r}
q<-ggplot(data3, aes(x=d, y=c, fill=a))+geom_bar(stat="identity")
```
```{r}
q
```
x-axis: average hourly earning, y-axis: total claim per industry
```{r}
g<-ggplot(data3, aes(d,c/100000, color=a))+labs(subtitle="Average hourly earnings vs. Claims", title="Bubble chart")+geom_jitter(aes(size=e))
```
```{r}
g
```

using bubble chart, x-axis: average hourly earning, y-axis: total claim, the size of bubble indicuates the industry 

Correlogram
```{r}
library(dplyr)
```

```{r}
library(corrplot)
```

```{r}
M<-cbind.data.frame(claim_sector$claims_total,claim_sector$claims_2016)
```
```{r}
M
```
```{r}
L<-cbind.data.frame(totalclaim,claim16)
```
```{r}
corr_matrix1<-cor(L)
```

```{r}
corr_matrix<-cor(M)
```
```{r}
corrplot(corr_matrix1, method = "number")
```
According to correlogram, there is strong positive relationship between total claim and claim of 2016. (They are correlated). 

```{r}
pie(claim_sector$claims_total, labels = claim_sector$naics_code, col=rainbow(length(claim_sector$naics_code)), main="Pie chart of industries claiming women sexaul harrassment")
```

```{r}
View(data3)
```

